---
title: "Analysis"
format: html
execute:
  echo: false
---

We have data about US voters in 1992, and we are trying to analyze it. We are not sure if representativeness holds. We are using a model from the brms package, using the categorical family, with the dependent variable being who was voted for. We modeled pres_vote, a character variable, as a multinomial logistic regression model. Women are most likely to support Clinton. A QOI is the probability of voting for a certain president, with a 95% confidence interval.

```{r,warning=FALSE}
#| label: setup
#| message: FALSE
library(primer.data)
library(tidyverse)
library(brms)
library(tidybayes)
library(gtsummary)
```

```{r}
#| label: cleaning
#| message: FALSE
nes_92 <- nes |> 
  filter(year == 1992) |> 
  select(sex, pres_vote) |> 
  drop_na() |> 
  mutate(pres_vote = case_when(
    pres_vote == "Democrat" ~ "Clinton",
    pres_vote == "Republican" ~ "Bush",
    pres_vote == "Third Party" ~ "Perot"
  ))
```

```{r}
#| label: model
#| cache: true
#| message: false
fit_nes<-brm(formula = pres_vote ~ sex, data = nes_92, family = categorical(), silent = 2, refresh = 0, seed = 76)
```

```{r,warning=FALSE}
#| label: table
tbl_regression(fit_nes)
```

```{r,warning=FALSE}
#| label: plot
ndata<-tibble(sex = c("Female", "Male"))

fit_nes|>
  add_epred_draws(newdata=ndata)|>
    select(sex,.category,.epred)|>
      ggplot(aes(x = .epred, fill = sex))+
      geom_histogram(bins=100)+
      facet_grid(~ .category)+
      scale_x_continuous(breaks=c(0.05, 0.3, 0.6),labels=scales::percent_format())+
      labs(title="Posterior for Expected Probability of Candidate Support Among Women",
           subtitle="Women are most likely to support Clinton",
           fill="Sex",
           y="Count",
           x="Posterior Probability of Expected Vote Probability")
```
